\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-25 doc/sw-system.tex
More AV comments...

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``sims'' from the \StageTwo training set. Insets indicate the
location of the simulated lens in each of these training images. Users needed to
click on these specific features in order to make a correct classification.}
\label{fig:training-gallery:sims}
\end{figure*}

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``duds'' from the \StageTwo training set. All of these
subjects were correctly classified by the community as not likely to contain
gravitational lenses; the insets merely indicate regions where $\sim10\%$ of the
volunteers clicked.} \label{fig:training-gallery:duds}
\end{figure*}

@@

\section{Classification Stages and Analysis}
\label{sec:swap}

@@

Each classification made is logged in a database, storing subject IDs,
(anonymous) volunteer IDs, a timestamp and the classification results.  The
{\it kind} of subject -- whether it is a training subject (a simulated lens
or a known non-lens) or a test subject (an unseen image drawn from the survey)
-- is also recorded. For all subjects, the positions of all Markers are
recorded, in pixel coordinates. For training subjects, we also store the
``classification'' of the subject as a lens, or a non-lens, and also the type
of object present in the image. These types are summarized in
\Tref{tab:objecttypes}.  This classification is used to provide instant
feedback, but is also the basic measurement used in a probabilistic
classification of every subject based on all image views to date.

While the \sw web app is live, and classifications are being made, we
perform an online analysis of the classifications,  updating a
probabilistic model of every (anonymous) volunteer's data, and also updating
the lens probability of each subject  (in both the training and test sets), on
a daily basis. This gives us a dynamic estimate of the posterior probability
for  any given  subject being a lens, given all classifications of it to date.
Assigning thresholds in this lens probability then allows us to make good
decisions about whether or not to retire a subject from the system, in order to
focus attention on new images.

@@

\item Each agent updates its confusion matrix elements based on the number of
times its volunteer has been right in each way while classifying subjects from
the training set, accounting for noise early on due to small number
statistics: $T$ is the set of all training images seen to date.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW Agent confusion matrix elements. At a particular
snapshot, 200 random Agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as the Agents' volunteers view more images. Yellow point size is
proprtional to the number of images classified; green point size shows
Agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\Fref{fig:swap:agent-probabilities} shows a random selection of Agents'
confusion matrix elements, as they were on a particular day towards the end of
the CFHTLS project. Many volunteers classify  only a small number of images,
and so their Agents' confusion matrix elements remain close to their initial
values of (0.5,0.5). As more images are classified (shown by the yellow point
size), the Agents' matrix elements tend to move towards higher values, as the
volunteers attain greater skill levels (green point sizes, see
\Sref{sec:results} below) and the Agent learns more about them. In this
quadrant, the Agents perceive their volunteers to be ``astute.'' This trend is
more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
the same sample of Agents as the number of images classified increases. The
histogram shows the distribution of classification number: a long tail to very
high ``effort'' can be seen.

>>>>

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``sims'' from the \StageTwo training set. The top right-hand corner insets indicate the
location of the simulated lens in each of these training images. Users needed to
click on these specific features in order to make a correct classification.}
\label{fig:training-gallery:sims}
\end{figure*}

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``duds'' from the \StageTwo training set. All of these
subjects were correctly classified by the community as not likely to contain
gravitational lenses; the top right-hand corner insets merely indicate regions where a minority ($\sim10\%$) of the
volunteers clicked.} \label{fig:training-gallery:duds}
\end{figure*}

@@

\section{Classification Analysis}
\label{sec:swap}

@@

Each classification made is logged in a database, storing subject IDs,
(anonymous) volunteer IDs, a timestamp and the classification results (the image pixel-coordinate positions of every marker placed).  The
``category'' of subject -- whether it is a ``training'' subject (a simulated
lens or a known non-lens) or a ``test'' subject (an unseen image drawn from the
survey) -- is also recorded. For all subjects, the positions of all Markers are
recorded, in pixel coordinates. For training subjects, we also store the
``kind'' of the subject as a lens (``sim''), or a non-lens (``dud''), and also
the ``flavor'' of lens object if one is present in the image (``lensed galaxy'',
``lensed quasar'' or ``cluster lens'').  This classification is used to provide
instant feedback, but is also the basic measurement used in a probabilistic
classification of every subject based on all image views to date.

While the \sw web app is live, and classifications are being made, we perform an
online analysis of the classifications,  updating a probabilistic model of every
(anonymous) volunteer's data, and also updating the posterior probability that
each subject (in both the training and test sets) contains a lens, on a daily
basis. This gives us a dynamic estimate of the posterior probability for  any
given  subject being a lens, given all classifications of it to date. Assigning
thresholds in this lens probability then allows us to make good decisions about
whether or not to retire a subject from the system, in order to focus attention
on new images.

@@

\item Each agent updates its confusion matrix elements based on the number of
times its volunteer has been right in each way (about both the sims and the
duds) while classifying subjects from the training set, accounting for noise
early on due to small number statistics: $T$ is the set of all training images
seen to date.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_probabilities.png}
\caption{Typical \SW Agent confusion matrix elements. At a particular
snapshot, 200 randomly-selected agents are shown distributed over the unit plane, with a
tendency to move towards the ``astute'' region in the upper right hand
quadrant as each agent's volunteer views more images. Yellow point size is
proprtional to the number of images classified; green point size shows
agent-perceived ``skill.''}
\label{fig:swap:agent-probabilities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\Fref{fig:swap:agent-probabilities} shows the confusion matrix elements of 200
randomly-selected agents, as they were on a particular day towards the end of
the CFHTLS project. Many volunteers classify  only a small number of images, and
so their agents' confusion matrix elements remain close to their initial values
of (0.5,0.5). As more images are classified (shown by the yellow point size),
the agents' matrix elements tend to move towards higher values, as the
volunteers attain greater skill levels (green point sizes, see
\Sref{sec:results} below) and the agent learns more about them. In this
quadrant, the agents perceive their volunteers to be ``astute.'' This trend is
more clearly seen in \Fref{fig:swap:agent-histories}, which shows the skill of
the same sample of agents as the number of images classified increases. The
histogram shows the distribution of classification number: a long tail to very
high ``effort'' can be seen.
